---
name: Gibran Hemani
position: "Senior Research Fellow, University of Bristol"
address: "8 Picton Mews, Bristol, BS6 5PB, United Kingdom"
phone: "+44(0)7930951876"
www: explodecomputer.com
email: explodecomputer@gmail.com
twitter: explodecomputer
github: explodecomputer
aboutme:
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")
```

```{r get data, include=FALSE}

## Employment
jobs <- read_csv(here::here("data", "jobs.csv"))

## Education
edu <- read_csv(here("data", "education.csv"))

## Publications - change google id here
scholar_id <- "6fC0BYYAAAAJ"
pubs <- scholar::get_publications(scholar_id) %>%
  dplyr::mutate(author = author %>% 
                as.character %>% 
                stringr::str_trim()) %>%
  dplyr::select(pubid, title, dplyr::everything())
write.csv(pubs, here("data", "pubs.csv"))
selected_pubs <- read_csv(here("data", "selected_pubs.csv"))

scholar_profile <- scholar::get_profile(scholar_id)
h_index <- scholar_profile$h_index
i10_index <- scholar_profile$i10_index


## Software
software <- read_csv(here::here("data", "software.csv")) %>% 
  arrange(desc(when)) 

## Dashboards
dashboards <- read_csv(here::here("data", "dashboards.csv")) %>% 
  arrange(desc(when)) 

## Teaching
teaching <- read_csv(here::here("data", "teaching.csv")) %>% 
  arrange(desc(when))

## Presentations
presentations <- read_csv(here::here("data", "presentations.csv")) %>% 
  arrange(desc(when))

## Training
training <- read_csv(here::here("data", "training.csv")) %>% 
  arrange(desc(end))

## Skills
skills <- read_csv(here::here("data", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  ungroup %>% 
  unique

## Service
service <- read_csv(here::here("data", "service.csv"))
```

# Education 
```{r}
detailed_entries(edu, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 where = loc,
                 with = uni,
                 why = details)

```

# Experience

```{r research}
jobs %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details)
```
# Skills

```{r}
skills %>% 
  detailed_entries(what = skill, with = category)
```
\pagebreak

# Training

```{r}
training %>% 
  detailed_entries(what = what, with = with, when = when, where = where, why = why)
```
# Teaching

```{r}
teaching %>% 
  detailed_entries(what = what, when = when, with = with, where = where, why = why)
```

# Publications

**First author**

```{r}
pubs %>% 
  dplyr::filter(first_author, !preprint) %>% 
  detailed_entries(
    what = title,
    when = as.character(year),
    with = author,
    where = journal, 
    .protect = TRUE
  )
```

**Non-first author**

```{r}
pubs %>% 
  dplyr::filter(!first_author, !preprint) %>% 
  detailed_entries(
    what = title,
    when = as.character(year),
    with = author,
    where = journal,
    .protect = TRUE
  )
```

**Preprints**

```{r}
pubs %>% 
  dplyr::filter(preprint) %>% 
  detailed_entries(
    what = title,
    when = as.character(year),
    with = author,
    where = journal, 
    .protect = TRUE
  )
```

*Updated programmatically each week. See [here](https://scholar.google.com/citations?user=GqZm90IAAAAJ&hl=en) for DOIs and citation details.*

\pagebreak

# Selected Software

**`R` Packages**

```{r}
software %>% 
  detailed_entries(what = what, with = package, when = when, where = where, why = why)
```

**Interactive tools**

```{r}
dashboards %>% 
  dplyr::mutate(with = what, 
                what = why) %>% 
  detailed_entries(what = what, with = with, when = when, where = where)
```

*See [my GitHub](https://github.com/seabbs/) for a complete overview of my software both released and in development.*

# Presentations

```{r}
presentations %>% 
  detailed_entries(what = what,
                   when = when,
                   with = with,
                   where = where,
                   why = why,
                   .protect = TRUE)
```

# Service

```{r}
service %>% 
  detailed_entries(with = type, why = details)
```
