---
name: Gibran Hemani
position: "Professor of statistical genetics, University of Bristol"
phone: "+44(0)7930951876"
www: gibranhemani.com
email: g.hemani@bristol.ac.uk
github: explodecomputer
aboutme:
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output:
  vitae::awesomecv:
    keep_tex: true
csl: "../resources/nature.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
library(tidyverse)
library(vitae)
library(bib2df)
library(here)
library(glue)

separate_why <- function(x)
{
  x %>%
    dplyr::mutate(why = strsplit(why, "\\. ")) %>%
    tidyr::unnest(why)
}
```

# Present Appointment

```{r employment}
jobs <- read_csv(here("data", "jobs.csv")) 

jobs[1,] %>%
  detailed_entries(
    what = role,
    when = glue("{start_date} to {end_date}"),
    with = company,
    where = where,
    why = details)
```

# Previous Appointments

```{r}
jobs[-1,] %>%
  detailed_entries(
    what = role,
    when = glue("{start_date} to {end_date}"),
    with = company,
    where = where,
    why = details)
```

# Academic Qualifications

```{r}
read_csv(here("data", "education.csv")) %>%
  detailed_entries(
    when = glue("{start_date} to {end_date}"),
    what = degree,
    where = loc,
    with = uni,
    why = details
)
```

# Special Awards, Honours and Distinctions

```{r awards}
read_csv(here("data", "awards.csv")) %>%
  arrange(desc(when)) %>%
  detailed_entries(
    with = what,
    what = why,
    when = when,
    where = where
)
```


# Publications summary

```{r}
load(here("data", "pubs.rdata"))

temp <- list(
  pubid="temp",
  title="The importance of family based sampling for biobanks",
  author="NM Davies, G Hemani, JM Neiderhiser, HC Martin, MC Mills, PM Visscher, L Yengo, AS Young, MC Keller",
  journal="Nature",
  number="In press",
  cites=0,
  year=2024,
  cid=NA
) %>% as.data.frame()

pubs <- bind_rows(temp, pubs)

convert_to_bib <- function(x)
{
  Encoding(x$author) <- "UTF-8"
  x$author <- iconv(x$author, "UTF-8", "UTF-8", sub="")
  x$pubid <- gsub("-", "", x$pubid)
  x$author <- sapply(x$author, function(string)
  {
    authors = trimws(unlist(strsplit(string, ",")))
    format_author = function(author) {
        words = trimws(unlist(strsplit(author, " ")))
        lastname = words[length(words)]
        first = words[!words %in% lastname]
        first = gsub("\\B[a-z]", "", first, perl = TRUE)
        first = paste(first, collapse = "")
        trimws(paste(first, lastname))
    }
    authors = sapply(authors, format_author)
    paste(authors, collapse = ", ")
  })

  tmpfile <- here("data", "pubs.bib")
  tibble(
    CATEGORY="ARTICLE",
    BIBTEXKEY=x$pubid,
    AUTHOR=
      strsplit(x$author, split=", ") %>%
      lapply(., function(i) {
        stringr::str_split(i, " ", n=2) %>%
        sapply(., function(j) {
          paste(rev(j), collapse=", ")
          }) %>%
        gsub("al, et", "others", .)
      }),
    TITLE=x$title,
    JOURNAL=x$journal,
    NUMBER=x$number,
    YEAR=x$year
  ) %>% bib2df::df2bib(file=tmpfile)
  b <- bibliography_entries(tmpfile)
  a <- gsub("\\\\leavevmode", "\\\\item \\\\leavevmode", readLines(tmpfile))
  writeLines(a, tmpfile)
  return(b)
}

pubs <- pubs %>% 
  filter(year >= 2018)
```


- H-index: **`r h_index`**
- i10-index: **`r i10_index`**
- Number of publications since indepdence (2018): **`r nrow(pubs)`**

A full list of publications since independence is at the end of the document.

# Research grants

```{r}
grants <- read_csv(here::here("data", "grants.csv")) %>%
  mutate(start=as.Date(start, format=c("%d/%m/%Y")), end=as.Date(end, format=c("%d/%m/%Y"))) %>%
  filter(awarded != "pending") %>%
  arrange(desc(start))

grant_totals <- grants %>% 
  group_by(role) %>% 
  summarise(n=n(), income=sum(amount * conversion), incomep = format(round(as.numeric(income), 2), nsmall=0, scientific=FALSE, big.mark=","))

grant_totals_current <- grants %>% 
  subset(., end > today()) %>%
  group_by(role) %>% 
  summarise(n=n(), income=sum(amount * conversion), incomep = format(round(as.numeric(income), 2), nsmall=0, scientific=FALSE, big.mark=","))


grantsf <- grants %>% 
  mutate(n=1:nrow(grants)) %>%
  group_by(n) %>%
  do({
    x <- .
    merge(
      x, 
      tibble(n=x$n[1],
        why=paste(
          "Amount: ", paste(format(round(as.numeric(x$amount)), nsmall=0, scientific=FALSE, big.mark=","), x$currency),
          "; Role: ", x$role,
          "; Dates: ", paste(x$start, "to", x$end),
          "; Proportion: ", x$perc),
        when=x$awarded
      )
    )
  })
```

Total income as PI, from `r subset(grant_totals, role=="PI")$n` grant(s): **`r subset(grant_totals, role=="PI")$incomep` GBP**

Total income as CI, from `r subset(grant_totals, role=="Co-I")$n` grant(s): **`r subset(grant_totals, role=="Co-I")$incomep` GBP**

Current income as PI, from `r subset(grant_totals_current, role=="PI")$n` grant(s): **`r subset(grant_totals_current, role=="PI")$incomep` GBP**

Current income as CI, from `r subset(grant_totals_current, role=="Co-I")$n` grant(s): **`r subset(grant_totals_current, role=="Co-I")$incomep` GBP**


```{r}
grantsf  %>%
  detailed_entries(with=title, why=why, when=when, what=funder)
```

# Indications of external recognition

## Editorships

```{r}
read_csv(here::here("data", "editorships.csv")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=what, when=when, with=with)
```

## Appointment to national or international bodies

```{r}
read_csv(here::here("data", "bodies.csv")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=what, when=when, with=with)
```

## Invitations for degree examinations

```{r}
read_csv(here::here("data", "degree_examination.csv")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=what, where=where, with=who, when=when)
```

## Invited lectures

```{r}
read_csv(here::here("data", "talks.csv")) %>% 
  arrange(desc(when)) %>%
  filter(when >= (now() %>% year() - 6)) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=what, with=who, when=when, where=type, why=details)
```

## Related administration

```{r}
read_csv(here::here("data", "research_management.csv")) %>%
  mutate(where = as.character(where)) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=with, where=where, with=what, when=when, why=why)
```

# Academic leadership and citizenship

```{r}
academic_leadership <- read_csv(here::here("data", "academic_leadership.csv")) %>%
  mutate(where = as.character(where), why = as.character(why)) %>%
  arrange(desc(when)) %>%
  separate_why()

# academic_leadership %>%
#   filter(type == "international") %>%
#   arrange(desc(when)) %>%
#   detailed_entries(what=as.character(what), where=where, with=with, when=when, why=why)
```

## Academic leadership in the University

```{r}
academic_leadership %>%
  filter(type == "university") %>%
  arrange(desc(when)) %>%
  detailed_entries(what=as.character(what), where=where, with=with, when=when, why=why)
```

## Professional activities outside the University

```{r}
academic_misc <- read_csv(here::here("data", "academic_misc.csv")) %>%
  arrange(desc(when))

academic_misc %>%
  filter(type=="professional") %>%
  brief_entries(what=what, when=when)
```

## Contributions to society

```{r}
academic_misc %>%
  filter(type=="society") %>%
  brief_entries(what=what, when=when)
```

## Entrepreneurship, enterprise and partnerships

```{r}
academic_misc %>%
  filter(type=="entrepreneurship") %>%
  brief_entries(what=what, when=when)
```

## Good citizenship

```{r}
academic_misc %>%
  filter(type=="citizenship") %>%
  brief_entries(what=what, when=when)
```
