---
name: Gibran Hemani
position: "Senior Research Fellow, University of Bristol"
address: "8 Picton Mews, Bristol, BS6 5PB, United Kingdom"
phone: "+44(0)7930951876"
www: explodecomputer.com
email: explodecomputer@gmail.com
twitter: explodecomputer
github: explodecomputer
aboutme:
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output: vitae::awesomecv
csl: "../resources/nature.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
source("../scripts/install.R")

separate_why <- function(x)
{
  x %>%
    dplyr::mutate(why = strsplit(why, "\\. ")) %>%
    tidyr::unnest(why)
}
```

# Academic Qualifications

```{r}
read_csv(here("data", "education.csv")) %>%
  detailed_entries(
    when = glue("{start_date} to {end_date}"),
    what = degree,
    where = loc,
    with = uni,
    why = details
)
```

# Employment

```{r employment}
read_csv(here("data", "jobs.csv")) %>%
  detailed_entries(
    what = role,
    when = glue("{start_date} to {end_date}"),
    with = company,
    where = where,
    why = details)
```

# Awards

```{r awards}
read_csv(here("data", "awards.csv")) %>%
  detailed_entries(
    with = what,
    what = why,
    when = when,
    where = where
)
```

# Publications

```{r}
load(here("data", "pubs.rdata"))
convert_to_bib <- function(x)
{
  Encoding(x$author) <- "UTF-8"
  x$author <- iconv(x$author, "UTF-8", "UTF-8", sub="")
  tmpfile <- here("data", "pubs.bib")
  tibble(
    CATEGORY="ARTICLE",
    BIBTEXKEY=x$pubid,
    AUTHOR=
      strsplit(x$author, split=", ") %>%
      lapply(., function(i) {
        stringr::str_split(i, " ", n=2) %>%
        sapply(., function(j) {
          paste(rev(j), collapse=", ")
          }) %>%
        gsub("al, et", "others", .)
      }),
    TITLE=x$title,
    JOURNAL=x$journal,
    NUMBER=x$number,
    YEAR=x$year,
    NOTE=x$info
  ) %>% bib2df::df2bib(file=tmpfile)
  bibliography_entries(tmpfile)
}
```

Selected publications organised by category are listed below. Full publication list on [google scholar](https://scholar.google.ca/citations?hl=en&user=6fC0BYYAAAAJ).

- H-index: **`r h_index`**
- i10-index: **`r i10_index`**
- Number of publications: **`r npubs`**

**Academic journal papers (refereed)**

```{r}
pubs %>% 
  dplyr::filter(type == "peer reviewed journal article") %>%
  convert_to_bib()
```

**Review articles**

```{r}
pubs %>% 
  dplyr::filter(type == "review article") %>%
  convert_to_bib()
```

**Selected published open source software**

```{r}
software <- read_csv(here::here("data", "software.csv")) 
bind_rows(
  software %>% mutate(why=what),
  software %>% mutate(why=where)
) %>% 
  arrange(desc(when), package) %>%
  detailed_entries(what = package, when = when, why = why)
```


**Forthcoming publications**

```{r}
pubs %>% 
  dplyr::filter(type == "forthcoming") %>%
  convert_to_bib()
```

# Research grants

```{r}
grants <- read_csv(here::here("data", "grants.csv")) %>%
  mutate(start=as.Date(start, format=c("%d/%m/%Y")), end=as.Date(end, format=c("%d/%m/%Y"))) %>%
  arrange(desc(start))

grant_totals <- grants %>% 
  group_by(role) %>% 
  summarise(n=n(), income=sum(amount * conversion), incomep = format(round(as.numeric(income), 2), nsmall=0, scientific=FALSE, big.mark=","))

grant_totals_current <- grants %>% 
  subset(., end > today()) %>%
  group_by(role) %>% 
  summarise(n=n(), income=sum(amount * conversion), incomep = format(round(as.numeric(income), 2), nsmall=0, scientific=FALSE, big.mark=","))


grantsf <- grants %>% 
  mutate(n=1:nrow(grants)) %>%
  group_by(n) %>%
  do({
    x <- .
    merge(
      x, 
      tibble(n=x$n[1],
        why=paste(
          "Amount: ", paste(format(round(as.numeric(x$amount)), nsmall=0, scientific=FALSE, big.mark=","), x$currency),
          "; Role: ", x$role,
          "; Dates: ", paste(x$start, "to", x$end),
          "; Proportion: ", x$perc),
        when=x$awarded
      )
    )
  })

grantsf  %>%
  detailed_entries(with=title, why=why, when=when, what=funder)
```


# Invited talks (last 3 years)

```{r}
read_csv(here::here("data", "talks.csv")) %>% 
  arrange(desc(when)) %>%
  filter(when >= (now() %>% year() - 3)) %>%
  arrange(desc(when)) %>%
  detailed_entries(what=what, with=who, when=when, where=type, why=details)
```

